&nbsp;

### 2021-03-23 README.Rmd
updated readme

The goal of SampleSizePlanner is to ...

## Installation

You can install the released version of SampleSizePlanner from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("SampleSizePlanner")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(SampleSizePlanner)
## basic example code
```

What is special about using `README.Rmd` instead of just `README.md`? You can include R chunks like so:

```{r cars}
summary(cars)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub!

>>>>

The goal of SampleSizePlanner is to help researchers determine the sample size for two group designs. The present application and R package offers 9 different sample size planning methods. In addition, the web application allows users to create a justification report for their sample size plan.

## Available sample size planning methods
* Accuracy In Parameter Estimation (AIPE)
* A-priori precision (APP)
* Predetermined sample size with Bayes factor
* Power curve
* Classical power calculation
* Interval Equivalence Bayes factor
* Region of Practical Equivalence (ROPE)
* Two One‐Sided Tests (TOST)
* Bayes Factor Design Analysis (BFDA)

## Usage

SampleSizePlanner can be used either via the web app or via R.

### Using the web app

You can use the app at [https://martonbalazskovacs.shinyapps.io/SampleSizePlanner/](https://martonbalazskovacs.shinyapps.io/SampleSizePlanner/).

You can alternatively run the app locally on your own computer by following these instructions:

Install the development version (SampleSizePlanner is not available from CRAN) from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("marton-balazs-kovacs/SampleSizePlanner")
```

Running the app.

``` r
SampleSizePlanner::run_app()
```

### Using the package

You can use the R package to determine the sample size with any of the 9 methods that present in the web app. However, it is not possible currently to generate a justification report from the R package. Please see the tutorial paper for example sample size justifications for each method.

## Note

The tutorial paper that presents the web application and R package is not reviewed yet.

## Code of Conduct

We are open to new ideas and feature requests.

Please note that the SampleSizePlanner project is released with a [Contributor Code of Conduct](https://marton-balazs-kovacs.github.io/SampleSizePlanner/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

### 2021-03-23 inst/app/www/about.Rmd
updated readme

### Available sample size planning methods
- AIPE [REF](link)
- APP [REF](link)
- BF threshold [REF](link)
- Power curve [REF](link)
- Traditional power calculation [REF](link)
- Interval equiv bf [REF](link)
- Rope [REF](link)
- TOST [REF](link)
- BFDA [REF](link)

### Contributors
- Don van Ravenzwaaij
- Rink Hoekstra
- Marton Kovacs
- Balazs Aczel

>>>>

### Contributors
- Don van Ravenzwaaij
- Marton Kovacs
- Rink Hoekstra
- Balazs Aczel
